
\begin{large}
% ------------------------------------------------------------------------------------

\bibitem{parisagreement} The Paris Agreement. (2015). \emph{UN Climate Change Conference}

\bibitem{climateact}  Climate Change Act, Intergenerational contract for the climate. (2021). \emph{Die bundesregierung, Energie und Klimaschutz.} 

\bibitem{energychartsinfo} Energy charts info. (2024). \emph{www.energycharts.info}.

\bibitem{sems} Moen, Roger. Solar energy management system. (1979). \emph{IEEE, $18^{th}$ Conference on Decision and Control}. 

\bibitem{evess} Mohammad et al. (2021). Integration of Electric Vehicles and Energy Storage System in Home Energy Management System with Home to Grid Capability. \emph{Energies 2021, 14, 8557}

\bibitem{milp} Hou et al. (2019). Smart Home Energy Management Optimization Method Considering ESS and PEV. \emph{ICIEA} 

\bibitem{dphev} ZHU et al. Optimization of rule-based energy management strategies for hybrid vehicles using
dynamic programming. (2021). \emph{Combustion Engines.}


\bibitem{qlearning}Lee et al. (2019). Reinforcement Learning-Based Energy Management of Smart Home with Rooftop Solar Photovoltaic System, Energy Storage System, and Home Appliances. \emph{ensors (Basel). 2019 Sep 12;19(18):3937}

\bibitem{drlgym}Specht et al. (2023) Deep reinforcement learning for the optimized operation of large amounts of distributed renewable energy assets. \emph{Energy and AI 11 (2023) 100215}

\bibitem{dataset} Ostermann et al, (2023). \emph{Bidirectional Electric Vehicles Field Trial Data Set}, NEIS 2023.

\bibitem{rlintro}Sutton et al. (2018). \emph{Reinforcement learning: An introduction} (2nd ed.). The MIT Press.

\bibitem{openaispin} OpenAI: Spinning Up in Deep Reinforcement Learning. (2018).

\bibitem{ppo}Schulman et al. (2017). \emph{Proximal Policy Optimization Algorithms}. arXiv:1707.06347v2.

\bibitem{sac}Tuomas et al. (2018). \emph{Soft Actor-Critic: Off-Policy Maximum Entropy Deep Reinforcement Learning with a Stochastic Actor}. arXiv:1801.01290v2.

\bibitem{td3}Fujimoto et al. (2018). \emph{Addressing Function Approximation Error in Actor-Critic Methods}. arXiv:1802.09477v3.

\bibitem{sb3}Raffin et al. (2021). \emph{Stable-Baselines3: Reliable Reinforcement Learning Implementations}. Journal of Machine Learning Research.

\bibitem{gymnasium}Towers et al. (2023). \emph{Gymnasium, An API standard for single-agent reinforcement learning environments}. Zenodo.

\bibitem{trpo}Schulman et al. (2017). Trust Region Policy Optimization \emph{arXiv:1502.05477v5}.

\bibitem{ddpg}Lillicrap et al. (2019). Continuous control with deep reinforcement learning. \emph{arXiv:1509.02971v6}.

\end{large}
% ------------------------------------------------------------------------------------

